Set up the TikZ in Emacs Org

### 2019-12-07 mstemc/index.tex
modify export-markdown-and-latex-using-emacs-org.org

% Intended LaTeX compiler: xelatex
\documentclass[koma,a4paper,utopia,10pt,listings-color,microtype,paralist,colorlinks]{org-article}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Set up the TikZ in Emacs Org File}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Set up the TikZ in Emacs Org File},
 pdfkeywords={},
 pdfsubject={An introduction to setup the TikZ environment in Emacs Org File.So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format. Furthermore, you can export the vector graph when latex is called and otherwise raster graph.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

An introduction to setup the TikZ environment in Emacs Org File.So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format. Furthermore, you can export the vector graph when latex is called and otherwise raster graph.

\section{config the header args}
\label{sec:org1e65b28}

@@

\begin{verbatim}
#+name: tutorial
#+header: :file "~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png"
#+header: :results raw :exports none :fit yes :border 0cm
#+header: :imagemagick t :iminoptions -density 400 :imoutoptions -geometry 400 -flatten
#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning, shapes.symbols, calc}")
#+begin_src latex
  \begin{tikzpicture}
    \node [circle, draw, fill=red!20] at (0,0) {1}
    child { node [circle, draw, fill=blue!30] {2}
      child { node [circle, draw, fill=green!30] {3} }
      child { node [circle, draw, fill=yellow!30] {4} }};
  \end{tikzpicture}
#+end_src
#+RESULTS: tutorial
[[file:../../img/tikz/tutorial.png]]
\end{verbatim}

The example begins with several lines containing \texttt{\#+header} which is sort of
clutter. we can put them in a file and include it at the beginning of the Org
file.
\section{generate results with different formats}
\label{sec:org92aa971}

By changing the extension of \texttt{:file} (which is \texttt{pdf} for
\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
body of the tikz code.
\section{export the results according to the backend}
\label{sec:org8166ca3}

@@

\section{the final workflow}
\label{sec:org6fc731d}

>>>>

% Intended LaTeX compiler: xelatex
\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Set up the TikZ in Emacs Org}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Set up the TikZ in Emacs Org},
 pdfkeywords={},
 pdfsubject={An introduction to setup the TikZ environment in Emacs Org File. So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format. Furthermore, you can export the vector graph when latex is called and otherwise raster graph.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

An introduction to setup the TikZ environment in Emacs Org File. So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format. Furthermore, you can export the vector graph when latex is called and otherwise raster graph.

\section{config the header args}
\label{sec:orgb7646ae}

@@

\begin{verbatim}
#+name: tutorial
#+header: :file "~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png"
#+header: :results raw :exports none :fit yes :border 0cm
#+header: :imagemagick t :iminoptions -density 400
#+header: :imoutoptions -geometry 400 -flatten
#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning,
           shapes.symbols, calc}")
#+begin_src latex
  \begin{tikzpicture}
    \node [circle, draw, fill=red!20] at (0,0) {1}
    child { node [circle, draw, fill=blue!30] {2}
      child { node [circle, draw, fill=green!30] {3} }
      child { node [circle, draw, fill=yellow!30] {4} }};
  \end{tikzpicture}
#+end_src
#+RESULTS: tutorial
[[file:../../img/tikz/tutorial.png]]
\end{verbatim}

The example begins with several lines containing \texttt{\#+header} which is sort of
clutter. we can put them in a file and include it at the beginning of the Org
file.
\section{generate results with different formats}
\label{sec:orgfa49106}

By changing the extension of \texttt{:file} (which is \texttt{pdf} for
\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
body of the tikz code.
\section{export the results according to the backend}
\label{sec:org6e31306}

@@

\section{the final workflow}
\label{sec:orgdf6c076}
